```{r}
#Percent of Carteret County Males Below the Poverty Line and Employed Map
mapview(carteret.combined.shape, zcol = "EmplydM", col.regions = c(paletteer_c("grDevices::Zissou 1", 30)), layer.name = "Percent of Carteret County Males Below the Poverty Line and Employed", label = carteret.combined.shape$NAMELSA)

#Percent of Carteret County Civilian Labor Force 16 Years and Over Below the Poverty Line and Employed Map
mapview(carteret.combined.shape, zcol = "CLF1YaO", col.regions = c(paletteer_c("grDevices::Zissou 1", 30)), layer.name = "Percent of Carteret County Civilian Labor Force 16 Years and Over Below the Poverty Line and Employed", label = carteret.combined.shape$NAMELSA)

#Percent of Carteret County Males Below the Poverty Line and Employed & Max Flooding Map
mapview(carteret.combined.maxflood.shape, zcol = "EmplydM", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Carteret County Males Below the Poverty Line and Employed", label = carteret.combined.maxflood.shape$NAMELSA)

#Percent of Carteret County Civilian Labor Force 16 Years and Over Below the Poverty Line and Employed & Max Flooding Map
mapview(carteret.combined.maxflood.shape, zcol = "CLF1YaO", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Carteret County Civilian Labor Force 16 Years and Over Below the Poverty Line and Employed", label = carteret.combined.maxflood.shape$NAMELSA)

#Percent of Carteret County Males Below the Poverty Line and Employed & Min Flooding Map
mapview(carteret.combined.min3flood.shape, zcol = "EmplydM", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Carteret County Males Below the Poverty Line and Employed", label = carteret.combined.min3flood.shape$NAMELSA)

#Percent of Carteret County Civilian Labor Force 16 Years and Over Below the Poverty Line and Employed & Min Flooding Map
mapview(carteret.combined.min3flood.shape, zcol = "CLF1YaO", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Carteret County Civilian Labor Force 16 Years and Over Below the Poverty Line and Employed", label = carteret.combined.min3flood.shape$NAMELSA)

#determined max flooding: 3.687
#determined least flooding: 0.012, 2.392, 3.043

#Population Below Poverty Line & Max Flooding Map
mapview(carteret.combined.maxflood.shape, zcol = "PpltbPL", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Carteret County Population Below Poverty Line", label = carteret.combined.maxflood.shape$NAMELSA, zoom=12) 

#Percent of Carteret County Below Poverty Line and Recieved Some College Education & Max Flooding Map
mapview(carteret.combined.maxflood.shape, zcol = "Scad_bpl", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Carteret County Below Poverty Line and Recieved Some College Education", label = carteret.combined.maxflood.shape$NAMELSA)

#Percent of Carteret County 25 Years and Older Below Poverty Line & Max Flooding Map
mapview(carteret.combined.maxflood.shape, zcol = "P2yao_bpl", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Carteret County 25 Years and Older Below Poverty Line", label = carteret.combined.maxflood.shape$NAMELSA)

#Population over 65 & Below Poverty Line & Min Flooding Map
mapview(carteret.combined.min3flood.shape, zcol = "X6_o_bpl", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Carteret County Population Over 65 and Below Poverty Line", label = carteret.combined.minflood.shape$NAMELSA)

#Population Below Poverty Line & Min Flooding Map
mapview(carteret.combined.min3flood.shape, zcol = "PpltbPL", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Carteret County Population Below Poverty Line", label = carteret.combined.minflood.shape$NAMELSA)

#Percent of Carteret County Below Poverty Line and Recieved Some College Education & Min Flooding Map
mapview(carteret.combined.min3flood.shape, zcol = "Scad_bpl", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Carteret County Below Poverty Line and Recieved Some College Education", label = carteret.combined.min3flood.shape$NAMELSA)

#Percent of Carteret County 25 Years and Older Below Poverty Line & Min Flooding Map
mapview(carteret.combined.min3flood.shape, zcol = "P2yao_bpl", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Carteret County 25 Years and Older Below Poverty Line", label = carteret.combined.min3flood.shape$NAMELSA)


#Asian Population Percent of Carteret County Map
mapview(carteret.combined.hurricane.shape, zcol = "Asian", col.regions = c(
paletteer_c("ggthemes::Red-Green-Gold Diverging", 30)), layer.name = "Asian Population Percent of Carteret County", label = carteret.combined.hurricane.shape$Asian)

#Percent of Carteret County Males Below the Poverty Line and Employed Map
mapview(carteret.combined.hurricane.shape, zcol = "EmployedMale", col.regions = c(paletteer_c("ggthemes::Temperature Diverging", 30)), layer.name = "Percent of Carteret County Males Below the Poverty Line and Employed", label = carteret.combined.hurricane.shape$NAMELSA)

#Percent of Carteret County Employed Map
mapview(carteret.combined.hurricane.shape, zcol = "PercentEmployed", col.regions = c(
paletteer_c("ggthemes::Red-Green-Gold Diverging", 30)), layer.name = "Percent of Carteret County Below the Poverty Line and Employed", label = carteret.combined.hurricane.shape$NAMELSA)


#Population Under 18 and Below Poverty Line & Min Hurricane Map
mapview(carteret.combined.minhurricane.shape, zcol = "Undr18b", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Population Under 18 Below Poverty Line in Min Annualized Hurricane Frequency Census Tracts", label = carteret.combined.minhurricane.shape$NAMELSA)

#Population Below Poverty Line & Min Hurricane Map
mapview(carteret.combined.minhurricane.shape, zcol = "PpltnPL", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Population Below Poverty Line in Min Annualized Hurricane Frequency Census Tracts", label = carteret.combined.minhurricane.shape$NAMELSA)

#Some college associates degree below poverty line & Min Hurricane Map 
mapview(carteret.combined.minhurricane.shape, zcol = "Smcllgs", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Population Below Poverty Line and Recieved Some College Education in Min Annualized Hurricane Frequency Census Tracts", label = carteret.combined.minhurricane.shape$NAMELSA)

#Percent of Carteret County Males Below the Poverty Line and Employed & Min Hurricane Map
mapview(carteret.combined.minhurricane.shape, zcol = "EmplydM", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Carteret County Males Below the Poverty Line and Employed in Min Annualized Hurricane Frequency Census Tracts", label = carteret.combined.minhurricane.shape$NAMELSA)

#Asian Population Percent of Min Hurricane Tracts Carteret County Map
mapview(carteret.combined.minhurricane.shape, zcol = "Asian", col.regions = c(
paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Asian Population Percent of Carteret County in Min Annualized Hurricane Frequency Census Tracts", label = carteret.combined.minhurricane.shape$Asian)

#Percent of Carteret County Employed Map
mapview(carteret.combined.maxhurricane.shape, zcol = "PercentEmployed", col.regions = c(
paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Population Below the Poverty Line and Employed in Max Annualized Hurricane Frequency Census Tracts", label = carteret.combined.maxhurricane.shape$NAMELSA)

#Asian Population Percent of Carteret County Map
mapview(carteret.combined.maxhurricane.shape, zcol = "Asian", col.regions = c(
paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Asian Population Percent of Carteret County in Max Annualized Hurricane Frequency Census Tracts", label = carteret.combined.maxhurricane.shape$Asian)

```{r more hurricane maps, echo=FALSE}
summary(carteret.combined.hurricane.shape$AnnlzHF)
#determining max hurricane: 3.0792
#determining least hurricane: 0.3870, 0.3974

#Annualized Hurricane Frequency in Carteret County Map
mapview(carteret.combined.hurricane.shape, zcol = "AnnualizedHurricaneFrequency", col.regions = c(
paletteer_c("ggthemes::Temperature Diverging", 30)), layer.name = "Annualized Hurricane Frequency in Carteret County", label = carteret.combined.hurricane.shape$NAMELSA)

#Population over 65 & Below Poverty Line & Max Hurricane Map
mapview(carteret.combined.maxhurricane.shape, zcol = "65overbelowpovertyline", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Population Over 65 and Below Poverty Line in Max Annualized Hurricane Frequency Census Tracts", label = carteret.combined.maxhurricane.shape$NAMELSA)

#Percent of Carteret County Below Poverty Line and Received Some College Education & Max Hurricane Map
mapview(carteret.combined.maxhurricane.shape, zcol = "Somecollegeassociatesdegreebelowpovertyline", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Population Below Poverty Line and Recieved Some College Education in Max Annualized Hurricane Frequency Census Tracts", label = carteret.combined.maxhurricane.shape$NAMELSA)

#Percent of Carteret County under 18 Below Poverty Line & Max Hurricane Map
mapview(carteret.combined.maxhurricane.shape, zcol = "Under18belowpovertyline", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Population Under 18 Below Poverty Line in Max Annualized Hurricane Frequency Census Tracts", label = carteret.combined.maxhurricane.shape$NAMELSA)

#Percent of Carteret County Males Below the Poverty Line and Employed & Max Hurricane Map
mapview(carteret.combined.maxhurricane.shape, zcol = "EmployedMale", col.regions = c(paletteer_d("ggthemes::Nuriel_Stone")), layer.name = "Percent of Carteret County Males Below the Poverty Line and Employed in Max Annualized Hurricane Frequency Census Tracts", label = carteret.combined.maxhurricane.shape$NAMELSA)

```

```